---
title: "Unit 1 - 3 Review Starter"
author: "Group 4"
date: "10/4/21"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sand_minerals <- read_csv("data/sand-minerals.csv")
location_descriptions <- read_csv("data/location-descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility-hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sand_minerals)
names(sand_minerals)
```
There are `r nrow(sand_minerals)` rows and `r ncol(sand_minerals)` variables.

Rows represent a mineral and location combination.

### Exercise 2

```{r inspect-other-dataframes}
glimpse(density)
variable.names(density)
variable.names(solubility_hardness)
glimpse(solubility_hardness)
glimpse(location_descriptions)
variable.names(location_descriptions)
```
There are `r nrow(density)` rows and `r ncol(density)` variables in the density dataframe.

There are `r nrow(solubility_hardness)` rows and `r ncol(solubility_hardness)` variables in the solubility hardness dataframe.

There are `r nrow(location_descriptions)` and `r ncol(location_descriptions)` variables in the location_descriptions dataframe.

In the density and solubility_hardness datasets, the rows are Quartz, Feldspar, and Biotite. In the location_description dataset, the rows are numbered 1-10 for the different locations.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
