---
title: "Unit 1 - 3 Review Starter"
author: "Group 4"
date: "10/4/21"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sand_minerals <- read_csv("data/sand-minerals.csv")
location_descriptions <- read_csv("data/location-descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility-hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sand_minerals)
names(sand_minerals)
```
There are `r nrow(sand_minerals)` rows and `r ncol(sand_minerals)` variables.

Rows represent a mineral and location combination.

### Exercise 2

```{r inspect-other-dataframes}
glimpse(density)
variable.names(density)
variable.names(solubility_hardness)
glimpse(solubility_hardness)
glimpse(location_descriptions)
variable.names(location_descriptions)
```
There are `r nrow(density)` rows and `r ncol(density)` variables in the density dataframe.

There are `r nrow(solubility_hardness)` rows and `r ncol(solubility_hardness)` variables in the solubility hardness dataframe.

There are `r nrow(location_descriptions)` and `r ncol(location_descriptions)` variables in the location_descriptions dataframe.

In the density and solubility_hardness datasets, the rows are Quartz, Feldspar, and Biotite. In the location_description dataset, the rows are numbered 1-10 for the different locations.

### Exercise 3

```{r join-mineral-properties}
sand_mineral_density <- left_join(sand_minerals, density)

sand_mineral_properties <- sand_mineral_density %>%
  left_join(solubility_hardness)
```
There are `r nrow(sand_mineral_density)` rows in the sand_mineral_density dataset and `r nrow(sand_minerals)` rows in the sand_minerals dataset. They have the same number of rows. 

### Exercise 4

```{r sand-grains-per-location}
sand_mineral_properties %>%
count(location)
```

```{r bottom-ten-rows-of-sand-per-location}
sand_mineral_properties %>%
slice(14:23)

```

```{r sand-grains-density}
sand_mineral_properties %>% 
  arrange(desc(density)) %>% 
  slice(14:23)
```

```{r first-and-last-columns}
sand_mineral_properties %>% 
  select(location, hardness) %>%
  slice(19:23)
```

```{r hardness-density-top5}
sand_mineral_properties %>%
  filter(!is.na(hardness)) %>%
  arrange(desc(density)) %>%
  slice(1:5)
```

### Exercise 5

```{r distinct-densities}
sand_mineral_properties %>%
distinct(density)
```

```{r count-minerals}
sand_mineral_properties %>%
  count(minerals)
```

```{r create-density-1000}
sand_mineral_properties %>%
  mutate(density_1000 = density / 1000)
```

```{r mean-density}
sand_mineral_properties %>%
  summarize(density_mean = mean(density))
```

```{r density-by-location}
sand_mineral_properties %>%
   group_by(location) %>%
  summarize(density_by_location = mean(density))
 
```


### Exercise 6

```{r sand-pivot}
sand_minerals %>% 
  pivot_wider() %>%
  pivot_longer(2)
```

